More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-02-06 2016-Weak-FH-Bisim/WeakBisim.tex
Quelques TODOs faciles avant reu

\noindent
\begin{minipage}{0.69\linewidth} 	Suppose that
   $A_1 = <\overline{\LTS_1},J,\mathcal{S}_1, s_0,
   \mathcal{T}_1>$ and $A_2 = <\overline{\LTS_2},J,\mathcal{S}_2,t_0, \mathcal{T}_2>$
   are open automata where the set
   of holes are equal %\LUDO{added:} 
   and of the same sort.  %\LUDO{changed:}

@@

%Where $\symb{Subst}(\Pred,\Post)$ is the parallel substitution of all
%assigned variables.
Two pNets are FH-bisimilar if there exist a relation between their associated 
automata that is an FH-bisimulation and their initial states are equivalent.
\TODO{Ludo: define are equivalent : is in the relation les valeurs des variables des 
etats initiaux verifient le predicat associe aux etats initiaux}
 \end{definition}
Classically, $\Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}$
applies in parallel the  
substitutions $\Post_{OT}$ and $\Post_{OT_x}$ (parallelism is crucial
inside each $\Post$ set but $\Post_{OT}$ is independent from
$\Post_{OT_x}$), applying the assignments of the involved rules.

@@

\LUDO{added congruence theorem below}
\begin{theorem}[Congruence]\label{thm-congr-eq}
	Consider an open pNet:
	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
	\overline{\symb{SV}}\myrangle$.
	Let $j_0\in J$ be a hole. Let $Q$ and $Q'$ be two FH-bisimilar pNets such that 
	$\Sortop(Q)=\Sortop(Q')=\Sort_{j_0}$\footnote{Note that $\Sortop(Q)=\Sortop(Q')$ is 
	ensured by 
	strong bisimilarity.}. Then 
	$\pNet[Q]_{j_0}$ and 
	$\pNet[Q']_{j_0}$ are FH-bisimilar.
\end{theorem}

@@

\TODO{Ludo: ask Simon for weak properties of Bip composition
  ``operators'' -- DONE!}

@@

\begin{lemma}[OT decomposition]\label{lem-decompose} 
	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose:
	\[ P[Q]_{j_0}  
		\models
		{\inferrule*[myfraction=\reddottedrule]
			{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I},
				\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTarrow {v}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with $Q$ ``moving'' \TODO{or is reduced?}, i.e. $J\cap\Holes(Q)\neq\emptyset$ or $I\cap L_Q\neq 
		\emptyset$.
		 Then there exist $v_Q$, $\Pred\,'$, $\Pred\,''$, 
		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\inferrule*[myfraction=\reddottedrule]
			{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\setminus L_Q},
				\{\xrightarrow{b_j}_j\}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {v}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
	\vspace{-2.2ex}\\\text{and~~}
		%\[
		Q\models{\inferrule*[myfraction=\reddottedrule]
			{\{s_i\xrightarrow{a_i}_i s_i'\}^{\,i\in I\cap L_Q},
				\{\xrightarrow{b_j}_j\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
				\Post\,''}
			{\ostate{s_i^{i\in L_Q}} \OTarrow {v_Q}
				\ostate{s_i'^{\,i\in L_Q}}}
		}%\]
		\end{mathpar}
		and  $\Pred\subst{v_Q\leftarrow b_{j_0}} =(\Pred\,'
		\land \Pred\,'')$, $\Post=\Post\,'\uplus 
		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
		$\Leaves(Q)$.
\end{lemma}

>>>>

\noindent
\begin{minipage}{0.69\linewidth} 	Suppose that
   $A_1 = <\overline{\LTS_1},J,\mathcal{S}_1, s_0,
   \mathcal{T}_1>$ and $A_2 = <\overline{\LTS_2},J,\mathcal{S}_2,t_0, \mathcal{T}_2>$
   are open automata where the set
   of holes are equal 
   and of the same sort.

@@

%Where $\symb{Subst}(\Pred,\Post)$ is the parallel substitution of all
%assigned variables.
Two pNets are FH-bisimilar if there exist a relation between their associated 
automata that is an FH-bisimulation and their initial states are in the relation, i.e. 
the predicate associated to the relation between the initial states is true.
\TODO{do we want formulas for this?}
 \end{definition}
Classically, $\Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}$
applies in parallel the  
substitutions $\Post_{OT}$ and $\Post_{OT_x}$ (parallelism is crucial
inside each $\Post$ set but $\Post_{OT}$ is independent from
$\Post_{OT_x}$), applying the assignments of the involved rules.

@@

\begin{theorem}[Congruence]\label{thm-congr-eq}
	Consider an open pNet:
	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
	\overline{\symb{SV}}\myrangle$.
	Let $j_0\in J$ be a hole. Let $Q$ and $Q'$ be two FH-bisimilar pNets such that 
	$\Sortop(Q)=\Sortop(Q')=\Sort_{j_0}$\footnote{Note that $\Sortop(Q)=\Sortop(Q')$ is 
	ensured by 
	strong bisimilarity.}. Then 
	$\pNet[Q]_{j_0}$ and 
	$\pNet[Q']_{j_0}$ are FH-bisimilar.
\end{theorem}

@@

@@

\begin{lemma}[OT decomposition]\label{lem-decompose} 
	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose:
	\[ P[Q]_{j_0}  
		\models
		{\inferrule*[myfraction=\reddottedrule]
			{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I},
				\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTarrow {v}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $I\cap L_Q\neq 
		\emptyset$, i.e. $Q$ takes part in the reduction.
		 Then there exist $v_Q$, $\Pred\,'$, $\Pred\,''$, 
		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\inferrule*[myfraction=\reddottedrule]
			{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\setminus L_Q},
				\{\xrightarrow{b_j}_j\}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {v}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
	\vspace{-2.2ex}\\\text{and~~}
		%\[
		Q\models{\inferrule*[myfraction=\reddottedrule]
			{\{s_i\xrightarrow{a_i}_i s_i'\}^{\,i\in I\cap L_Q},
				\{\xrightarrow{b_j}_j\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
				\Post\,''}
			{\ostate{s_i^{i\in L_Q}} \OTarrow {v_Q}
				\ostate{s_i'^{\,i\in L_Q}}}
		}%\]
		\end{mathpar}
		and  $\Pred\subst{v_Q\leftarrow b_{j_0}} =(\Pred\,'
		\land \Pred\,'')$, $\Post=\Post\,'\uplus 
		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
		$\Leaves(Q)$.
\end{lemma}
